Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-04-28 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
updated abstract.

\documentclass[journal=jpcbfk,manuscript=article]{achemso}
\usepackage{CJK}

@@

  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux, and thus solute selectivity, in macroscopic length pores.

@@

  Next, we generalize Markov state models, treating the
  configurational states of the system as a Markov process where each
  state has distinct transport properties. For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that both models reasonably reproduce
  the MSDs calculated from MD simulations. However, qualitative differences 
  between MD and Markov state dependent model-generated trajectories may limit 
  its usefulness.

  Finally, we demonstrate how one can use these models to 
  estimate flux of a solute across a macroscopic-length pore and, based on 
  those quantities, the membrane's selectivity towards each solute. This work 
  helps to connect microscopic chemically-dependent solute motions that do not
  follow simple diffusive behavior with macroscopic membrane performance.

@@

  \graphicspath{{./figures/arxiv_figures/}}

>>>>

\documentclass[journal=jctcce,manuscript=article]{achemso}
\usepackage{CJK}

@@

  Mathematically modeling complex transport phenomena can be a
  powerful tool
  %MRS: this paper doesn't really address identifying transport, though, does it?  Although (other) modeling can be 
  %MRS: useful, putting it in the abstract implies mechanism identification is in this paper.
  %for identifying transport mechanisms and predicting
  %macroscopic properties.  
  for extracting important physical
  information from molecular simulation.  In this study, we present
  two new approaches to use stochastic time series modeling to predict
  long-time scale behavior and macroscopic properties from molecular
  simulation which can be generalized to other molecular systems
  where complex diffusion occurs.

  In this study, we use two different stochastic time series modeling approaches
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane in order to predict solute mean squared displacements (MSDs)
  and solute flux, and thus solute selectivity, in macroscopic length pores.

@@

  Next, we present an approach that generalizes Markov state models,
  treating the configurational states of the system as a Markov
  process where each state has distinct transport properties. For each
  state and transition between states, we parameterize the
  distribution and temporal correlation structure of positional
  fluctuations as a means of characterization and to allow us to
  predict solute MSDs. We show that both models reasonably reproduce
  the MSDs calculated from MD simulations. However, qualitative
  differences between MD and Markov state dependent model-generated
  trajectories may limit its usefulness.

  Finally, we demonstrate how one can use these models to estimate
  flux of a solute across a macroscopic-length pore and, based on
  those quantities, the membrane's selectivity towards each
  solute. This work therefore helps to connect microscopic,
  chemically-dependent solute motions that do not follow simple
  diffusive behavior with long-time scale behavior, in an approach
  generalizable to many kinds of molecular systems with complex dynamics.

@@

  \graphicspath{{./figures/}}
